Silent pessimists - researchers' perceptions of malaria eradication and implications for health spending

### 2017-10-10 paper.Rmd
finished heckman

## The need for the wisdom of crowds

@@

Additionally, one could argue that assessing likelihood and time frame of eradication is too important, subjective and complex a task to be left to only powerful individuals or small panels and committees. It requires the “wisdom of crowds.” Measuring consensus and discord among disease-specific researchers from a variety of disciplines can serve as a barometer of (informed) opinion, both guiding resources and identifying areas of concern [@Keenan2013].

@@

```{r, results = 'asis'}
stargazer(ols1, heck1, ml1,
          header = FALSE,
          # se=list(cse(ols1),NULL,NULL),
          title="Regression on years until eradication", 
          type="text",
          df=FALSE, digits=4)
# summary(ols1)
# summary(heck1)

@@

```{r}
# Define function for analyzing the years_n columns
years_n <- function(n){
  x <- df %>%
    dplyr::select_(paste0('years_', n)) 
  names(x) <- 'likelihood'
  result <- x %>%
    group_by(likelihood) %>%
    tally %>%
    mutate(p = n / sum(n) * 100) %>%
    filter(!is.na(likelihood))

@@

```{r, fig.height = 4.5, fig.width = 4.5}
# Get averages per area
results_list <- list()
dist_list <- list()
year_list <- list()

small_areas <- areas_df$area[areas_df$count >= 15]
small_areas <- areas[1:12]
for (i in 1:length(small_areas)){
  this_area <- small_areas[i]
  sub_data <- df[df[,paste0('area_', gsub(' ', '_', this_area))],]
  this_df <- data_frame(area = this_area,
                        avg = mean(sub_data$years, na.rm = TRUE),
                        med = median(sub_data$years, na.rm = TRUE))
  dist_df <- data_frame(area = this_area,
                        val = sub_data$years)
  numberfy <- function(x){
    ifelse(x == '0%', 0,
                ifelse(x == '1-20%', 10,
                       ifelse(x == '21-40%', 30,
                              ifelse(x == '41-60%', 50,
                                     ifelse(x == '61-80%', 70,
                                            ifelse(x == '81-99%', 90,
                                                   ifelse(x == '100%', 100, NA)))))))

@@

ggplot(data = results) + 
  geom_violin(aes(x = bb,
           y = ranking),
           fill = 'orange',
              alpha = 0.6) +
  geom_jitter(aes(x = bb,
           y = ranking),
           color = 'black',
           with = 0.4,
           height = 0.4,
              alpha = 0.3,
              size = 1) +
  theme_publication(base_size = 10) +
  labs(x = 'WHO Building block',
       y = 'Ranking',
       title = 'Perceived areas needing attention',
       subtitle = 'Small points: jittered individual responses; large triangles: averages') +
  geom_point(data = results_agg,
             aes(x = bb,
                 y = avg),
             size = 5,
             pch = 17,
             color = 'black',
             alpha = 0.8)
```

>>>>

## The need for a broad concensus

@@

Additionally, one could argue that assessing likelihood and time frame of eradication is too important, subjective and complex a task to be left to only powerful individuals or small panels and committees. It requires the aggregation of multiple points of view. Measuring consensus and discord among disease-specific researchers from a variety of disciplines can serve as a barometer of (informed) opinion, both guiding resources and identifying areas of concern [@Keenan2013].

@@

```{r, results = 'markup'}
# stargazer(ols1, heck1, ml1,
#           header = FALSE,
#           # se=list(cse(ols1),NULL,NULL),
#           title="Regression on years until eradication", 
#           type="text",
#           df=FALSE, digits=4)
# # summary(ols1)
# # summary(heck1)

@@

```{r}
# Define function for analyzing the years_n columns
years_n <- function(n){
  x <- df %>%
    filter(responded) %>%
    dplyr::select_(paste0('years_', n)) 
  names(x) <- 'likelihood'
  result <- x %>%
    group_by(likelihood) %>%
    tally %>%
    mutate(p = n / sum(n) * 100) %>%
    filter(!is.na(likelihood))

@@

```{r, fig.height = 4.5, fig.width = 4.5}
# Get averages per area
results_list <- list()
dist_list <- list()
year_list <- list()
areas_df <- areas_df %>% arrange(desc(count))
small_areas <- areas_df$area[1:12]
for (i in 1:length(small_areas)){
  this_area <- small_areas[i]
  sub_data <- df[df[,paste0('area_', gsub(' ', '_', this_area))],]
  this_df <- data_frame(area = this_area,
                        avg = mean(sub_data$years, na.rm = TRUE),
                        med = median(sub_data$years, na.rm = TRUE))
  dist_df <- data_frame(area = this_area,
                        val = sub_data$years)
  numberfy <- function(x){
    ifelse(x == '0%', 0,
                ifelse(x == '1-20%', 10,
                       ifelse(x == '21-40%', 30,
                              ifelse(x == '41-60%', 50,
                                     ifelse(x == '61-80%', 70,
                                            ifelse(x == '81-99%', 90,
                                                   ifelse(x == '100%', 100, NA)))))))

@@

ggplot(data = results) + 
  geom_violin(aes(x = bb,
           y = ranking),
           fill = 'orange',
              alpha = 0.6) +
  geom_jitter(aes(x = bb,
           y = ranking),
           color = 'black',
           with = 0.4,
           height = 0.4,
              alpha = 0.3,
              size = 1) +
  theme_publication(base_size = 10) +
  labs(x = 'WHO Building block',
       y = 'Ranking',
       title = 'Perceived areas needing attention',
       subtitle = 'Small points: jittered individual responses; large triangles: averages') +
  geom_point(data = results_agg,
             aes(x = bb,
                 y = avg),
             size = 5,
             pch = 17,
             color = 'black',
             alpha = 0.8) +
  ylim(0, 6)
ggsave('~/Desktop/figure2.png', height = 4, width = 5.5)
```
